Metrics

### 2024-04-16 src/plots.Rmd
Remove cods <10 samples for cod perf plots

    # Prepare boxplot data
    coddata <- out %>%
        select(
            Model,
            starts_with(sprintf("PCCC %s COD Agree ", aref))
        ) %>%
        rename_at(
             vars(-Model),
             ~gsub(sprintf("PCCC %s COD Agree ", aref), "", .)
        ) %>%
        filter(!str_detect(Model, "&")) %>% # remove multi models
        pivot_longer( # transform to long format
            cols = -Model,
            names_to = "COD",
            values_to = "PCCC"
        ) %>%
        mutate( # rename cod with counts
            "COD" = recode(`COD`, !!!cod_remap)
        ) %>%
        group_by(`COD`) %>%
        mutate( # Make values less than 0 equal to 0
            PCCC = if_else(PCCC <= 0, 0, PCCC)
        ) %>%
        mutate( # Add min, mid, and max model names to label
            "PCCC Min" = if_else(
                PCCC <= min(PCCC) + 0.05,
                paste0(
                    Model,
                    if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
                ),
                NA
            ),
            "PCCC Max" = if_else(
                PCCC >= max(PCCC) - 0.05,
                paste0(
                    Model,
                    if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
                ),
                NA
            ),
            "PCCC Mid" = if_else(
                is.na(`PCCC Min`) & is.na(`PCCC Max`),
                paste0(Model, "\n(", round(PCCC, 2), ")"),
                NA
            ),
            "PCCC Min" = if_else( # Combine into one row if close PCCC
                `PCCC` == min(PCCC),
                if_else(
                    sum(!is.na(`PCCC Min`)) > 1,
                    paste0(na.omit(`PCCC Min`), collapse = "\n"),
                    paste0(
                        str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\)", ""),
                        collapse = "\n"
                    )
                ),
                NA
            ),
            "PCCC Max" = if_else(
                `PCCC` == max(PCCC),
                if_else(
                    sum(!is.na(`PCCC Max`)) > 1,
                    paste0(na.omit(`PCCC Max`), collapse = "\n"),
                    paste0(str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\)", ""),
                           collapse = "\n")
                ),
                NA
            )
        )

@@

    # Plot boxplot
    codplot <- coddata %>%
        ggplot(aes(x = COD, y = PCCC)) +
        geom_boxplot(
            linewidth = 0.5,
            width = 0.25
        ) +
        geom_text(
            aes(label = `PCCC Min`),
            color = "#4d4d4d",
            size = 2.5,
            hjust = 1,
            position = position_nudge(y = -0.12)
        ) +
        geom_text(
            aes(label = `PCCC Max`),
            color = "#4d4d4d",
            size = 2.5,
            hjust = 0,
            position = position_nudge(y = 0.12)
        ) +
        stat_summary( # min pccc txt on boxplot
            geom = "text",
            fun = min,
            aes(label = sprintf("%1.2f", after_stat(y))),
            position = position_nudge(y = -0.06),
            size = 3
        ) +
        stat_summary( # max pccc txt on boxplot
            geom = "text",
            fun = max,
            aes(label = sprintf("%1.2f", after_stat(y))),
            position = position_nudge(y = 0.06),
            size = 3
        ) +
        labs(
            x = atitle,
            y = "PCCC (0=Low, 1=High)"
        ) +
        ylim(-0.3, 1.3) +
        coord_flip() +
        theme_minimal() +
        theme(
            panel.grid = element_blank(),
            axis.line = element_blank(),
            axis.line.y = element_blank(),
            axis.title.x = element_text(margin = margin(t = 10)),
            axis.title.y = element_text(margin = margin(r = 10)),
            axis.line.x = element_line(
                color = "black",
                arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
            )
        )

>>>>

    # Get cods with less than 10 samples
    cod_low_counts <- cod_counts[cod_counts < 10]
    cod_low_perc <- sapply(cod_low_counts, function(x) {
        xprop <- (x / arows) * 100
        if (xprop < 1) {
            return("<1")
        } else {
            return(as.character(round(xprop)))
        }
    })
    cod_low_label <- paste0(
        names(cod_low_counts),
        " (n=", cod_low_counts, ", ", cod_low_perc, "%)",
        collapse = ", "
    )

    # Prepare boxplot data
    coddata <- out %>%
        select(
            Model,
            starts_with(sprintf("PCCC %s COD Agree ", aref))
        ) %>%
        rename_at(
             vars(-Model),
             ~gsub(sprintf("PCCC %s COD Agree ", aref), "", .)
        ) %>%
        filter(!str_detect(Model, "&")) %>% # remove multi models
        pivot_longer( # transform to long format
            cols = -Model,
            names_to = "COD",
            values_to = "PCCC"
        ) %>%
        mutate( # rename cod with counts
            "COD" = recode(`COD`, !!!cod_remap)
        ) %>%
        group_by(`COD`) %>%
        mutate( # Make values less than 0 equal to 0
            PCCC = if_else(PCCC <= 0, 0, PCCC)
        ) %>%
        mutate( # Add min, mid, and max model names to label
            "PCCC Min" = if_else(
                PCCC <= min(PCCC) + 0.05,
                paste0(
                    Model,
                    if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
                ),
                NA
            ),
            "PCCC Max" = if_else(
                PCCC >= max(PCCC) - 0.05,
                paste0(
                    Model,
                    if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
                ),
                NA
            ),
            "PCCC Mid" = if_else(
                is.na(`PCCC Min`) & is.na(`PCCC Max`),
                paste0(Model, "\n(", round(PCCC, 2), ")"),
                NA
            ),
            "PCCC Min" = if_else( # Combine into one row if close PCCC
                `PCCC` == min(PCCC),
                if_else(
                    sum(!is.na(`PCCC Min`)) > 1,
                    paste0(na.omit(`PCCC Min`), collapse = "\n"),
                    paste0(
                        str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\)", ""),
                        collapse = "\n"
                    )
                ),
                NA
            ),
            "PCCC Max" = if_else(
                `PCCC` == max(PCCC),
                if_else(
                    sum(!is.na(`PCCC Max`)) > 1,
                    paste0(na.omit(`PCCC Max`), collapse = "\n"),
                    paste0(str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\)", ""),
                           collapse = "\n")
                ),
                NA
            )
        ) %>%
        filter( # remove CODs with <10 samples
            !str_detect(COD, paste0("^", names(cod_low_counts), collapse = "|"))
        )

@@

    # Plot boxplot
    codplot <- coddata %>%
        ggplot(aes(x = COD, y = PCCC)) +
        geom_boxplot(
            linewidth = 0.5,
            width = 0.25
        ) +
        geom_text(
            aes(label = `PCCC Min`),
            color = "#4d4d4d",
            size = 2.5,
            hjust = 1,
            position = position_nudge(y = -0.12)
        ) +
        geom_text(
            aes(label = `PCCC Max`),
            color = "#4d4d4d",
            size = 2.5,
            hjust = 0,
            position = position_nudge(y = 0.12)
        ) +
        stat_summary( # min pccc txt on boxplot
            geom = "text",
            fun = min,
            aes(label = sprintf("%1.2f", after_stat(y))),
            position = position_nudge(y = -0.06),
            size = 3
        ) +
        stat_summary( # max pccc txt on boxplot
            geom = "text",
            fun = max,
            aes(label = sprintf("%1.2f", after_stat(y))),
            position = position_nudge(y = 0.06),
            size = 3
        ) +
        labs(
            x = atitle,
            y = "PCCC (0=Low, 1=High)",
            caption = paste0("CODs removed (n<10): ", cod_low_label, ".")
        ) +
        ylim(-0.3, 1.3) +
        coord_flip() +
        theme_minimal() +
        theme(
            panel.grid = element_blank(),
            axis.line = element_blank(),
            axis.line.y = element_blank(),
            axis.title.x = element_text(margin = margin(t = 10)),
            axis.title.y = element_text(margin = margin(r = 10)),
            axis.line.x = element_line(
                color = "black",
                arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
            ),
            plot.caption = element_text(size = 6, face = "italic")
        )
